P4IRS: An Intermediate Representation and Compiler for Parallel and Performance-Portable Particle Simulations

### 2024-07-04 sage_latex_template/manuscript.tex
minor
Signed-off-by: Rafael Ravedutti <rafael.r.ravedutti@fau.de>

We also show weak-scaling results to demonstrate P4IRS scaling capabilities.
For this we use regular domain-partitioning since these experiments do not require sophisticated load-balancing algorithms (Copper lattice is an homogeneous test-case in all dimensions, and Settling Spheres can obtain acceptable weak-scaling by regularly partitioning the domain in X and Y dimensions).
We use double floating-point precision and display results when enabling and disabling Newton's 3rd Law optimization (half neighbor-lists).
For \ac{MD} simulations, we show results with the Verlet Lists optimization strategy since it is widely employed the field, while for \ac{DEM} we display results with the Linked Cells data-structure because particles are rigid bodies and actually need to be in contact for contributions to be computed, hence there are no significant advantages of using Verlet Lists.

>>>>

We also show weak-scaling results to demonstrate P4IRS scaling capabilities.
For this we use regular domain-partitioning since these experiments do not require sophisticated load-balancing algorithms (Copper lattice is an homogeneous test-case in all dimensions, and Settling Spheres can obtain acceptable weak-scaling by regularly partitioning the domain in X and Y dimensions).
We use double floating-point precision and display results when enabling and disabling Newton's 3rd Law optimization (half neighbor-lists).
For \ac{MD} simulations, we show results with the Verlet Lists optimization strategy since it is widely employed in the field, while for \ac{DEM} we display results with the Linked Cells data-structure because particles represent rigid bodies that need to be in contact for their contributions to be computed.
Since the amount of contacts is typically way less than atomic interactions, there are no significant advantages of using the Verlet Lists data structure.
